---
title: "Project-01"
author: "Dominic Henry"
date: "3/8/2021"
geometry: margin=2cm
output: pdf_document
---

## Setting up twitter api with twitteR
 
```{r}

# install.packages("twitteR")
library("twitteR")

consumer_key <- 'Ch9jskjCH77J7fCyfSqClPlK5'
consumer_secret <- 'PDRion0it91KJ4FAvGoCWhveyIVfsuZYPDz4jclriHy0zbxf6l'

access_token <- '1588970316-6ABtNLKgBCoDNS5fq4bLAcf27F1UmRx74XNiPqF'
access_secret <- 'PFemqiLO0WyqLmBAHDZMm7YF2smbLSC1GTEKtFeEw7GV8'

setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)

```

### Note

When using the twitteR package function searchTwitter it allows for the selection
flag that only retrieves tweets of a given language. Thus for task two no additional filtering for English tweets was necessary. 

### Retrieving tweets with the word "beverage" and Cleaning (March 8, 2021)

```{r}

# beverageTweets <- searchTwitter("beverage", n=8000, lang="en")
# beverageTweetsDf <- twListToDF(beverageTweets)
head(beverageTweetsDf, 5)

```

### Retrieving tweets with the word "party" and Cleaning (March 9, 2021)

```{r}

# partyTweets <- searchTwitter("party", n=8000, lang="en")
# partyTweetsDf <- twListToDF(partyTweets)
head(partyTweetsDf, 5)

```

### Retrieving Tweets with the word "beer" and Cleaning (March 13, 2021)

```{r}

# beerTweets <- searchTwitter("beer", n=8000, lang="en")
# beerTweetsDf <- twListToDF(beerTweets)
head(beerTweetsDf, 5)

```

### Retrieving Tweets with the word "concert" and Cleaning (March 14, 2021)

```{r}

# concertTweets <- searchTwitter("concert", n=8000, lang="en")
# concertTweetsDf <- twListToDF(concertTweets)
head(concertTweetsDf, 5)

```


### Retriving additional user related data.

twitteR does not include certain user data with given tweets, so I used an additional function to facilitate getting and appending user information for each tweet.

**Removing all duplicate tweets for each dataset**

Utilizing tidyverse/dplyr to remove all duplicate tweets from each datasets.
Removing duplicates prior to requesting additional user data should reduce the amount of requests made to Twitter's API.
```{r}
library(tidyverse)

beverageTweetsDf <- beverageTweetsDf %>% distinct(text, .keep_all = TRUE)
print(paste("Beverage Tweets Duplicates: ", 8000 - nrow(beverageTweetsDf)))

partyTweetsDf <- partyTweetsDf %>% distinct(text, .keep_all = TRUE)
print(paste("Party Tweets Duplicates: ", 8000 - nrow(partyTweetsDf)))

beerTweetsDf <- beerTweetsDf %>% distinct(text, .keep_all = TRUE)
print(paste("Beer Tweets Duplicates: ", 8000 - nrow(beerTweetsDf)))

concertTweetsDf <- concertTweetsDf %>% distinct(text, .keep_all = TRUE)
print(paste("Concert Tweets Duplicates: ", 8000 - nrow(concertTweetsDf)))

```

**Creating new columns needed**

```{r}

beverageTweetsDf$location <- NA
beverageTweetsDf$followers_count <- NA
beverageTweetsDf$friends_count <- NA
beverageTweetsDf$account_lang <- NA

partyTweetsDf$location <- NA
partyTweetsDf$followers_count <- NA
partyTweetsDf$friends_count <- NA
partyTweetsDf$account_lang <- NA

beerTweetsDf$location <- NA
beerTweetsDf$followers_count <- NA
beerTweetsDf$friends_count <- NA
beerTweetsDf$account_lang <- NA

concertTweetsDf$location <- NA
concertTweetsDf$followers_count <- NA
concertTweetsDf$friends_count <- NA
concertTweetsDf$account_lang <- NA

```

**Getting user details for each dataset**

Utilizing lookUpUsers function from twitteR package for each dataset. 

```{r}

beverageUsersInfoDf <- twListToDF(lookupUsers(beverageTweetsDf$screenName))
head(beverageUsersInfoDf, 5)

partyUsersInfoDf <- twListToDF(lookupUsers(partyTweetsDf$screenName))
head(partyUsersInfoDf, 5)

beerUsersInfoDf <- twListToDF(lookupUsers(beerTweetsDf$screenName))
head(beerUsersInfoDf, 5)

concertUsersInfoDf <- twListToDF(lookupUsers(concertTweetsDf$screenName))
head(concertUsersInfoDf, 5)

```

**Binding data from each userinfo data frame with tweets data frame**

If a given user is not found, then all user related data retrieved will be marked with *NA*.
Iterating over the smaller user list should make populating initial list of tweets faster. 

```{r}

# beverageTweetsDf
for(screenName in beverageUsersInfoDf$screenName){
  filterRows <- beverageTweetsDf$screenName == screenName
  user <- beverageUsersInfoDf[beverageUsersInfoDf$screenName == screenName,]
  
  beverageTweetsDf[filterRows,]$location <- user$location
  beverageTweetsDf[filterRows,]$followers_count <- user$followersCount
  beverageTweetsDf[filterRows,]$friends_count <- user$friendsCount
  beverageTweetsDf[filterRows,]$account_lang <- user$lang
}

# partyTweetsDf
for(screenName in partyUsersInfoDf$screenName){
  filterRows <- partyTweetsDf$screenName == screenName
  user <- partyUsersInfoDf[partyUsersInfoDf$screenName == screenName,]
  
  partyTweetsDf[filterRows,]$location <- user$location
  partyTweetsDf[filterRows,]$followers_count <- user$followersCount
  partyTweetsDf[filterRows,]$friends_count <- user$friendsCount
  partyTweetsDf[filterRows,]$account_lang <- user$lang
}

# beerTweetsDf
for(screenName in beerUsersInfoDf$screenName){
  filterRows <- beerTweetsDf$screenName == screenName
  user <- beerUsersInfoDf[beerUsersInfoDf$screenName == screenName,]
  
  beerTweetsDf[filterRows,]$location <- user$location
  beerTweetsDf[filterRows,]$followers_count <- user$followersCount
  beerTweetsDf[filterRows,]$friends_count <- user$friendsCount
  beerTweetsDf[filterRows,]$account_lang <- user$lang
}

# concertTweetsDf
for(screenName in concertUsersInfoDf$screenName){
  filterRows <- concertTweetsDf$screenName == screenName
  user <- concertUsersInfoDf[concertUsersInfoDf$screenName == screenName,]
  
  concertTweetsDf[filterRows,]$location <- user$location
  concertTweetsDf[filterRows,]$followers_count <- user$followersCount
  concertTweetsDf[filterRows,]$friends_count <- user$friendsCount
  concertTweetsDf[filterRows,]$account_lang <- user$lang
}

head(beverageTweetsDf, 5)
head(partyTweetsDf, 5)
head(beerTweetsDf, 5)
head(concertTweetsDf, 5)

```

### Extracting only neccessary columns from dataset

**Changing field names to camel case**

```{r}

beverageTweetsDf$screen_name <-  beverageTweetsDf$screenName
beverageTweetsDf$user_id <- beverageTweetsDf$id
beverageTweetsDf$created_at <- beverageTweetsDf$created
beverageTweetsDf$favourite_count <- beverageTweetsDf$favoriteCount
beverageTweetsDf$retweet_count <- beverageTweetsDf$retweetCount

partyTweetsDf$screen_name <-  partyTweetsDf$screenName
partyTweetsDf$user_id <- partyTweetsDf$id
partyTweetsDf$created_at <- partyTweetsDf$created
partyTweetsDf$favourite_count <- partyTweetsDf$favoriteCount
partyTweetsDf$retweet_count <- partyTweetsDf$retweetCount

beerTweetsDf$screen_name <-  beerTweetsDf$screenName
beerTweetsDf$user_id <- beerTweetsDf$id
beerTweetsDf$created_at <- beerTweetsDf$created
beerTweetsDf$favourite_count <- beerTweetsDf$favoriteCount
beerTweetsDf$retweet_count <- beerTweetsDf$retweetCount

concertTweetsDf$screen_name <-  concertTweetsDf$screenName
concertTweetsDf$user_id <- concertTweetsDf$id
concertTweetsDf$created_at <- concertTweetsDf$created
concertTweetsDf$favourite_count <- concertTweetsDf$favoriteCount
concertTweetsDf$retweet_count <- concertTweetsDf$retweetCount

```

**Extracting key features from each group tweets**

```{r}

key_features <- c("text", "screen_name", "user_id", "created_at", 
                  "favourite_count", "retweet_count", "location", 
                  "followers_count", "friends_count", "account_lang")

```



```{r}

beverageTweetsDf <- beverageTweetsDf[,key_features]
head(beverageTweetsDf)

partyTweetsDf <- partyTweetsDf[,key_features]
head(partyTweetsDf)

beerTweetsDf <- beerTweetsDf[,key_features]
head(beerTweetsDf)

concertTweetsDf <- concertTweetsDf[,key_features]
head(concertTweetsDf)

```

### Storing datasets to csv file

```{r}

write.csv(beverageTweetsDf, 'beverage_2021Mar08_DominicHenry.csv')
write.csv(partyTweetsDf, 'party_2021Mar09_DominicHenry.csv')
write.csv(beerTweetsDf, 'beer_2021Mar13_DominicHenry.csv')
write.csv(concertTweetsDf, 'concert_2021Mar14_DominicHenry.csv')

```

### Tweets Dataset Details

**Create function show details for each tweet dataset**

```{r}

tweetDatasetDetails <- function(df){
  dataframeName <- deparse(substitute(df))
  
  print(dataframeName)
  print(paste("Number of tweets in ", dataframeName, ": ", nrow(df)))
  
  # User with screen name with most followers
  max_followers_count <- max(df$followers_count, na.rm = TRUE)
  screen_name_max_followers_count <- df[
    (df$followers_count == max_followers_count &
       !is.na(df$followers_count)),]$screen_name
  
  print(
    paste(
      "Most followers ", 
      max_followers_count, 
      " in ", dataframeName, ": ", 
      screen_name_max_followers_count))
  
  # User with screen name with most retweets
  max_retweet_count <- max(df$retweet_count, na.rm = TRUE)
  screen_name_max_retweet_count <- df[
    (df$retweet_count == max_retweet_count &
       !is.na(df$retweet_count)),]$screen_name
  
  print(
    paste(
      "Most Retweets ", 
      max_retweet_count, " in ", 
      dataframeName, ": ", screen_name_max_retweet_count))
  
  
  # Location with with the most tweets.
  # The first value will most likely be Missing Values
  # Thus the second value will contain the location with the most 
  # amount of tweets for the dataset
  location_tweets <- df %>% filter(!is.na(location)) %>% count(location, sort = TRUE)
  print(paste(
    "Location with most tweets being ", 
    location_tweets[2,]$n,"is: ", 
    location_tweets[2,]$location))
  
  
}

```

**Dataset Details**

```{r}

tweetDatasetDetails(beverageTweetsDf)
tweetDatasetDetails(partyTweetsDf)
tweetDatasetDetails(beerTweetsDf)
tweetDatasetDetails(concertTweetsDf)

```