---
title: "Project Part 02"
author: "Dominic Henry | Dineah Cohen"
date: "4/2/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## Authors' Information

- Dominic Henry - 620118591
- Dineah Cohen - 620117662

## Tweet Data Analysis
```{r}
library("SnowballC")
library("tm")
library("syuzhet")
```

## Reading Datasets

```{r}

beverageDF1 <- read.csv("datasets/beverage_2021Mar08_DominicHenry.csv")
beverageDF2 <- read.csv("datasets/beverage_2021Mar13_Cohen.csv")

beerDF1 <- read.csv("datasets/beer_2021Mar13_DominicHenry.csv")
beerDF2 <- read.csv("datasets/beer_2021Mar08_Cohen.csv")

concertDF1 <- read.csv("datasets/concert_2021Mar14_DominicHenry.csv")
concertDF2 <- read.csv("datasets/concert_2021Mar14_Cohen.csv")

partyDF1 <- read.csv("datasets/party_2021Mar09_DominicHenry.csv")
partyDF2 <- read.csv("datasets/party_2021Mar09_Cohen.csv")

```

## Making columns identical for Beverage tweets
```{r}
beverageDF1 <- beverageDF1[1:10]
beverageDF2 <- beverageDF2[1:10]

names(beverageDF1)[6] <- "favourite_count"
```

## Making columns identical for Beer tweets
```{r}
beerDF1 <- beerDF1[1:10]
beerDF2 <- beerDF2[1:10]

names(beerDF1)[6] <- "favourite_count"
```

## Making columns identical for Concert tweets
```{r}
concertDF1 <- concertDF1[1:10]
concertDF2 <- concertDF2[1:10]

names(concertDF1)[6] <- "favourite_count"
```

## Making columns identical for Party tweets
```{r}
partyDF1 <- partyDF1[1:10]
partyDF2 <- partyDF2[1:10]

names(partyDF1)[6] <- "favourite_count"
```

# Merging datasets
```{r}
mergedBeverageTweets<- rbind(beverageDF1, beverageDF2)
mergedBeerTweets <- rbind(beerDF1, beerDF2)
mergedConcertTweets<- rbind(concertDF1, concertDF2)
mergedPartyTweets <- rbind(partyDF1, partyDF2)
```


# Removing duplicate tweets
```{r}
library(tidyverse)
mergedBeerTweets <- mergedBeerTweets[!duplicated(mergedBeerTweets$text),]
mergedBeverageTweets <- mergedBeverageTweets[!duplicated(mergedBeerTweets$text),]
mergedConcertTweets <- mergedConcertTweets[!duplicated(mergedConcertTweets$text),]
mergedPartyTweets <- mergedPartyTweets[!duplicated(mergedPartyTweets$text),]
```


# Descriptive Statistics

## Concert statistics
```{r}
summary(mergedConcertTweets)
```

## Beer statistics
```{r}
summary(mergedBeerTweets)
```

## Beverage statistics
```{r}
summary(mergedBeverageTweets)
```

## Party statistics
```{r}
summary(mergedPartyTweets)
```

# Sentiment Analysis

## Dominant Emotion in Canada
```{r}
canadaTweets <- mergedBeverageTweets[mergedBeverageTweets$location == 'Canada', "text"]
canadaTweets <- gsub("https.*","", canadaTweets)
canadaTweets <- gsub("#.*","", canadaTweets)
canadaTweets <- gsub("@.*","", canadaTweets)
canadaTweets <- gsub("[^\x01-\x7F]", "", canadaTweets)
canadaEmotions <- get_nrc_sentiment(canadaTweets)

# Putting each tweet with its score
canadaTweets.data <- cbind (canadaTweets, canadaEmotions)

canada.anticipation <- sum(canadaEmotions$anticipation)
cat("Canada anticipation score: ", canada.anticipation, "\n")

canada.anger <- sum(canadaEmotions$anger)
cat("Canada anger score: ", canada.anger, "\n")

canada.disgust <- sum(canadaEmotions$disgust)
cat("Canada disgust score: ", canada.disgust, "\n")

canada.fear <- sum(canadaEmotions$fear)
cat("Canada fear score: ", canada.fear, "\n")

canada.joy <- sum(canadaEmotions$joy)
cat("Canada joy score: ", canada.joy, "\n")

canada.sadness <- sum(canadaEmotions$sadness)
cat("Canada sadness score: ", canada.sadness, "\n")

canada.surprise <- sum(canadaEmotions$surprise)
cat("Canada surprise score: ", canada.surprise, "\n")

canada.trust <- sum(canadaEmotions$trust)
cat("Canada trust score: ", canada.trust, "\n")
```

These results indicate that the dominant emotions in Canada are Trust and Joy, the scores were 12 and 11 respectively.


## Dominant Emotion in the United States
```{r}
unitedStatesTweets <- mergedBeverageTweets[mergedBeverageTweets$location == 'United States', "text"]
unitedStatesTweets <- gsub("https.*","", unitedStatesTweets)
unitedStatesTweets <- gsub("#.*","", unitedStatesTweets)
unitedStatesTweets <- gsub("@.*","", unitedStatesTweets)
unitedStatesTweets <- gsub("[^\x01-\x7F]", "", unitedStatesTweets)
unitedStatesEmotions <- get_nrc_sentiment(unitedStatesTweets)

unitedStatesTweets.data <- cbind (unitedStatesTweets, unitedStatesEmotions)

unitedStates.anticipation <- sum(unitedStatesEmotions$anticipation)
cat("United States anticipation score: ", unitedStates.anticipation, "\n")

unitedStates.anger <- sum(unitedStatesEmotions$anger)
cat("United States anger score: ", unitedStates.anger, "\n")

unitedStates.disgust <- sum(unitedStatesEmotions$disgust)
cat("United States disgust score: ", unitedStates.disgust, "\n")

unitedStates.fear <- sum(unitedStatesEmotions$fear)
cat("United States fear score: ", unitedStates.fear, "\n")

unitedStates.joy <- sum(unitedStatesEmotions$joy)
cat("United States joy score: ", unitedStates.joy, "\n")

unitedStates.sadness <- sum(unitedStatesEmotions$sadness)
cat("United States sadness score: ", unitedStates.sadness, "\n")

unitedStates.surprise <- sum(unitedStatesEmotions$surprise)
cat("United States surprise score: ", unitedStates.surprise, "\n")

unitedStates.trust <- sum(unitedStatesEmotions$trust)
cat("United States trust score: ", unitedStates.trust, "\n")
```

These results indicate that the dominant emotions in the United States are Trust and Joy, both scores were 50.


## Dominant emotion in beverage dataset
```{r}
beverageDf.text <- gsub("http.*","",mergedBeverageTweets$text)
beverageDf.text <- gsub("https.*","", beverageDf.text)
beverageDf.text <- gsub("#.*","", beverageDf.text)
beverageDf.text <- gsub("@.*","", beverageDf.text)
beverageDf.text <- gsub("[^\x01-\x7F]", "", beverageDf.text)
beverageDf.emotions <- get_nrc_sentiment(beverageDf.text)
```

```{r}
colSums(beverageDf.emotions)
```
According to the column sums, the dominant emotions in the Beverage dataset are Trust and Joy.


## Overall sentiments in tweets regarding the word "beverage"
```{r}
beverageSentiment <- mean(get_sentiment(beverageDf.text))
print(beverageSentiment)
```
From the sentiment score it can be deduced that the sentiment is Positive. This is due to the score being greater than 0.


## Overall sentiments in tweets regarding the word "concert"
```{r}
concertDF.text <- gsub("http.*","",mergedConcertTweets$text)
concertDF.text <- gsub("https.*","", concertDF.text)
concertDF.text <- gsub("#.*","", concertDF.text)
concertDF.text <- gsub("@.*","", concertDF.text)
concertDF.text <- gsub("[^\x01-\x7F]", "", concertDF.text)

concertSentiment <- mean(get_sentiment(concertDF.text))
print(concertSentiment)
```
From the sentiment score it can be deduced that the sentiment is Positive. This is due to the score being greater than 0.


## Preparing consumer structured data

### Reading consumer dataset

```{r}

consumerDF <- read.csv("datasets/consumer_pt02_2021.csv.csv")

```

### Data Exploration of consumer dataset

```{r}

summary(consumerDF)

```
Various numerical fields are character fields, which need to be converted to perform proper data manipulation.

**Fields that need to be formatted**

- Unit.Cost
- Total.Revenue
- Units.Sold
- Unit.Price
- Total.Cost
- Total.Profit

```{r}

consumerDF$Unit.Cost <- as.double(consumerDF$Unit.Cost)
consumerDF$Total.Revenue <- as.double(consumerDF$Total.Revenue)
consumerDF$Units.Sold <- as.integer(consumerDF$Units.Sold)
consumerDF$Unit.Price <- as.double(consumerDF$Unit.Price)
consumerDF$Total.Cost <- as.double(consumerDF$Total.Cost)
consumerDF$Total.Profit <- as.double(consumerDF$Total.Profit)

summary(consumerDF)

```
Many of the rows also contain missing values, which either need to be updated or removed if necessary to perform analysis.

### Checking for possible outliers in dataset

**Using histograms**
```{r}

hist(consumerDF$Unit.Cost)
hist(consumerDF$Total.Revenue)
hist(consumerDF$Units.Sold)
hist(consumerDF$Unit.Price)
hist(consumerDF$Total.Cost)
hist(consumerDF$Total.Profit)

```

No apparent outliers

**Using boxplots**

```{r}

boxplot(consumerDF$Unit.Cost, horizontal=T)
boxplot(consumerDF$Total.Revenue, horizontal=T)
boxplot(consumerDF$Units.Sold, horizontal=T)
boxplot(consumerDF$Unit.Price, horizontal=T)
boxplot(consumerDF$Total.Cost, horizontal=T)
boxplot(consumerDF$Total.Profit, horizontal=T)

```

Based on the boxplots we can more accurately see outliers present in the
attributes for `Total.Revenue`, `Total.Cost` and `Total.Profit`

### Cleaning Dataset

**Removing Records**

Excluding records that don't have Unit.Price, Units.Sold, Unit.Cost. These
fields are required to compute other attributes within the dataset such as
Total.Cost, Total.Revenue and Total.Profit.

```{r}

consumerDF <- consumerDF[!is.na(consumerDF$Unit.Price),]
consumerDF <- consumerDF[!is.na(consumerDF$Units.Sold),]
consumerDF <- consumerDF[!is.na(consumerDF$Unit.Cost),]

summary(consumerDF)

```

**Updating Calculated Fields**

Calculating Total Revenue for records with missing values

```{r}

consumerDF$Total.Revenue[is.na(consumerDF$Total.Revenue)] <- consumerDF$Units.Sold[is.na(consumerDF$Total.Revenue)] * consumerDF$Unit.Price[is.na(consumerDF$Total.Revenue)]

```

Calculating Total Cost for records with missing values

```{r}

consumerDF$Total.Cost[is.na(consumerDF$Total.Cost)] <- consumerDF$Units.Sold[is.na(consumerDF$Total.Cost)] * consumerDF$Unit.Cost[is.na(consumerDF$Total.Cost)]

```

Calculating Total Profit for records with missing values

```{r}

consumerDF$Total.Profit[is.na(consumerDF$Total.Profit)] <- consumerDF$Total.Revenue[is.na(consumerDF$Total.Profit)] * consumerDF$Total.Cost[is.na(consumerDF$Total.Profit)]

```

**Looking at summary data for updated fields**

```{r}

summary(consumerDF$Total.Revenue)
summary(consumerDF$Total.Cost)
summary(consumerDF$Total.Profit)

```

All fields updated, so no missing values are present in dataset, for further
calculations.

**Why Records with outliers are not being fixed**

Based on the dataset there are different categories of consumer products being
compared, thus their will be different values present in the dataset that may
on average cost more than certain consumer items, but may be average if compared
in the same category.

```{r}

unique(factor(consumerDF$X))

```

### Dataset Reformating

**Updating column name X to be Consumer.Category**

This is being done so that the column accurately represents what is being stored
in that attribute field.

```{r}

consumerDF$Consumer.Category <- factor(consumerDF$X)
consumerDF$X <- NULL

```

**Updating various columns to be factors**

```{r}

consumerDF$Country <- factor(consumerDF$Country)
consumerDF$Sales.Channel <- factor(consumerDF$Sales.Channel)
consumerDF$Order.Priority <- factor(consumerDF$Order.Priority)

```

### Final Summary of Consumer Data

```{r}

summary(consumerDF)

```

Missing values have been removed, and dataset columns have been formatted.

## Structured Data Analysis/Modeling

Filtering out Consumer Categories to only have beverages.

```{r}

consumerDF <- consumerDF[consumerDF$Consumer.Category == "Beverages",]
nrow(consumerDF)
View(consumerDF)

```

Number of records that fall under Beverages category is: `r nrow(consumerDF)`


## Average spent on beverages in each country

```{r}
uniqueCountries <- unique(consumerDF$Country)

for (country in uniqueCountries){
  cat(country, " - ", mean(consumerDF$Total.Cost[consumerDF$Country == country ]), "\n")
}
```

## Country that has the highest spending on beverages
Determining the country which spends the most on beverage requires the sum of the Total.Cost
for each country
```{r}
# Sum of total costs for beverages per country
beverageCostSum <- aggregate (consumerDF$Total.Cost, by= list(consumerDF$Country), FUN= sum)

# Getting the maximum total cost
beverageCostSum$Group.1[which.max(beverageCostSum$x)]
```

Based on the findings above, Yemen has highest spending cost for beverages.


## Country that consumes the most beverages

Determining the country which consumes the most beverage requires the sum of the Units.Sold
for each country
```{r}
beveragesConsumed <- aggregate (consumerDF$Units.Sold, by= list(consumerDF$Country), FUN= sum)
beveragesConsumed$Group.1[which.max(beveragesConsumed$x)]
```
From the results it shows that Yemen is also the country with the highest consumption of beverages.


## Average profit from sale of beverages in each country
```{r}
for (country in uniqueCountries){
  cat(country,":", mean(consumerDF$Total.Profit[consumerDF$Country == country]),"\n")
}
```


## Recommendations

## Beverage unit Prediction
