---
title: "Project Part 02"
author: "Dominic Henry | Dineah Cohen"
date: "4/2/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Authors' Information

- Dominic Henry - 620118591   
- Dineah Cohen - 620117662

## Tweet Data Analysis

## Making columns identical for Beverage tweets
```{r}
beverageDF1 <- beverageDF1[1:10]
beverageDF2 <- beverageDF2[1:10]

names(beverageDF1)[6] <- "favourite_count"
```

## Making columns identical for Beer tweets
```{r}
beerDF1 <- beerDF1[1:10]
beerDF2 <- beerDF2[1:10]

names(beerDF1)[6] <- "favourite_count"
```

## Making columns identical for Concert tweets
```{r}
concertDF1 <- concertDF1[1:10]
concertDF2 <- concertDF2[1:10]

names(concertDF1)[6] <- "favourite_count"
```

## Making columns identical for Party tweets
```{r}
partyDF1 <- partyDF1[1:10]
partyDF2 <- partyDF2[1:10]

names(partyDF1)[6] <- "favourite_count"
```

## Merging datasets
```{r}
mergedBeverageTweets<- rbind(beverageDF1, beverageDF2)
mergedBeerTweets <- rbind(beerDF1, beerDF2)
mergedConcertTweets<- rbind(concertDF1, concertDF2)
mergedPartyTweets <- rbind(partyDF1, partyDF2)
```

#Removing duplicate tweets

#Descriptive Statistics


## Preparing consumer structured data

## Structured Data Analysis/Modeling

## Recommendations

## Beverage unit Prediction